The \Prob

### 2013-03-04 bikes/bikes.tex
bikes: discuss optimality

\begin{figure}[h]
	\bf d=0\space d=0.5\space d=1\space d=1.5\space d=2
	\includegraphics[width=0.5\textwidth]{x0.png}\\
	\includegraphics[width=0.5\textwidth]{x1.png}\\
	\includegraphics[width=0.5\textwidth]{x2.png}\\
	\includegraphics[width=0.5\textwidth]{x3.png}\\
	\includegraphics[width=0.5\textwidth]{x4.png}\\
	\caption{The solution for $n,k=2,1$.}
	\label{fig:sol}
\end{figure}

@@

@@

Without loss of generality we say that $d$ is $n$ units of distance away.

>>>>

\begin{figure}[t]
	\bf d=0\space d=0.5\space d=1\space d=1.5\space d=2
	\includegraphics[width=0.5\textwidth]{x0.png}\\
	\includegraphics[width=0.5\textwidth]{x1.png}\\
	\includegraphics[width=0.5\textwidth]{x2.png}\\
	\includegraphics[width=0.5\textwidth]{x3.png}\\
	\includegraphics[width=0.5\textwidth]{x4.png}\\
	\caption{The solution for $n,k=2,1$.}
	\label{fig:sol}
\end{figure}

@@

Formally we say that the {\em bicycle allocation} for this case is that person $0$ (the blue one, if you're reading this electronically or printed in color) rides bike $0$ for distances between $0$ and $1$, and person $1$ (the red one, if same) rides it for distances between $1$ and $2$. For short, we write:
\begin{eqnarray*}
	p_0 &=& b_0[0,1] \\
	p_1 &=& b_0[1,2]
\end{eqnarray*}

@@

Without loss of generality, let us say that $d$ is $n$ units of distance away (i.e., the same as the number of people).
Before presenting a general allocation policy, some observations about the problem:
\begin{enumerate}
	\setlength{\itemsep}{-0.5em}
	\item A total of $n^2$ distances will be traveled. A total of $nk$ distances will be biked. It is pointless for bikes to go backwards.
	\item By symmetry, in an optimal solution, each person will bike $k$ distance and walk $n-k$ distance. This also means that fractional distances (less than $1/n$ of the total distance) need not be considered as places to mount/dismount.
	\item No more than $k$ people can ride for any given distance unit $[i,i+1]$. If any fewer than $k$ people rode this way, the bikes would be under-utilised. This allows us to check both validity and optimality.
	\item The optimal (minimum) total travel time is $k/b + (n-k)/w$. The optimal (maximum) average speed is $nbw/(kw+bn-bk)$.
	% TODO: Discuss epsilon.
\end{enumerate}
